\documentclass[11pt]{amsart}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{array}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!55!black,
  citecolor=blue!55!black,
  urlcolor=blue!55!black,
  pdftitle={Certified Finite Positivity Bands for a Riemann Xi-Defect Kernel via Endpoint Moment Bounds},
  pdfauthor={Leonard van Hemert}
}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\sinhc}{\operatorname{sinhc}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\dd}{\,\mathrm{d}}

\title[Certified finite positivity bands]{Certified Finite Positivity Bands for a Riemann $\Xi$-Defect Kernel via Endpoint Moment Bounds}
\author{Leonard van Hemert}
\date{20 July 2026}

\begin{document}

\begin{abstract}
Let $\Xi(z)=\xi(\frac12+iz)$ and let $\Phi$ denote the positive even
Riemann theta kernel in its full-line Fourier representation.  We study the
two-variable cosine transform
\begin{align*}
C_y(x)&=\iint_{\R^2}(u+v)^2\sinhc(y(u+v))\Phi(u)\Phi(v)\\
&\hspace{5em}{}\times\cos(x(u-v))\dd u\dd v,
\qquad 0\leq y\leq\tfrac12.
\end{align*}
The Hermite--Biehler defect of $E=\Xi+i\Xi'$ equals $2yC_y(x)$.  We derive
exact endpoint formulas for the even moments of the positive measure defining
$C_y$, bound the normalized moments by strict cross-endpoint ratios, and
integrate a global degree-ten Taylor minorant for cosine.  Outward-rounded
Arb computation then proves
\[
C_y(x)>0\qquad
\left(0\leq y\leq\tfrac12,\ |x|\leq R_{10}\right),
\]
where
\[
7.0362433<R_{10}<7.0362434.
\]
The certificate uses no zero enumeration.  The result is finite: it neither
proves the Riemann Hypothesis nor improves existing finite-height zero
verification.  We identify the unproved all-orders estimate that the
cross-endpoint method would require for unbounded positivity bands.
\end{abstract}

\maketitle

\section{Introduction}

Write
\begin{equation}\label{eq:xi-definition}
\xi(s)=\frac12s(s-1)\pi^{-s/2}\Gamma(s/2)\zeta(s),
\qquad
\Xi(z)=\xi\!\left(\frac12+iz\right).
\end{equation}
The completed function satisfies
\begin{equation}\label{eq:functional-equation}
\xi(s)=\xi(1-s),
\end{equation}
and $\Xi$ is real entire and even.  The Jacobi transformation gives the
full-line representation
\begin{equation}\label{eq:fourier}
\Xi(z)=\int_{\R}\Phi(u)e^{izu}\dd u,
\end{equation}
where, in the normalization used here,
\begin{equation}\label{eq:phi}
\Phi(u)=\sum_{n=1}^{\infty}
\left(4\pi^2n^4e^{9|u|/2}-6\pi n^2e^{5|u|/2}\right)
e^{-\pi n^2e^{2|u|}}.
\end{equation}
For $u\geq0$, each summand is positive because
\[
4\pi^2n^4e^{9u/2}-6\pi n^2e^{5u/2}
=2\pi n^2e^{5u/2}\left(2\pi n^2e^{2u}-3\right)>0.
\]
The Jacobi transformation makes the extension in \eqref{eq:phi} even and
smooth.  The kernel also satisfies a bound
\begin{equation}\label{eq:decay}
0<\Phi(u)\leq C e^{9|u|/2}
\exp\!\left(-\frac{\pi}{2}e^{2|u|}\right)
\end{equation}
for a fixed $C>0$.

Moment inequalities, Fourier criteria, and Hermite--Biehler formulations for
$\Xi$ have a substantial history.  Csordas, Norfolk, and Varga proved
P\'olya--Tur\'an inequalities for Taylor coefficients \cite{CNV1986}.
Csordas and Varga proved strict concavity of
$t\mapsto\log\Phi(\sqrt t)$ and obtained broad moment inequalities
\cite{CV1988}.  Their later work developed Hermite--Biehler and generalized
Laguerre criteria \cite{CV1989,CV1990}.  Coffey and Csordas gave another proof
of logarithmic concavity and related moment inequalities \cite{CC2013}, while
Csordas studied positive-definite associated kernels and isolated global
positivity conditions equivalent to the Riemann Hypothesis \cite{C2015}.

The contribution here is narrower.  We combine moments at $y=0$ and
$y=\frac12$ to obtain one explicit polynomial lower bound for a two-variable
defect kernel, uniformly over the closed $y$-interval.  The endpoint moments
are values of finite combinations of derivatives of $\xi$ at $0$ and
$\frac12$, so Arb can certify them without locating zeros.  The first positive
root of the resulting polynomial gives the stated finite band.

The zero consequence is not a record.  Platt and Trudgian rigorously verified
the Riemann Hypothesis through height $3\cdot10^{12}$ \cite{PT2021}.  The
interest of the present result lies in the moment certificate and its uniform
kernel inequality, rather than the small numerical height of the corollary.

\section{The defect kernel}

Set
\[
\sinhc t=
\begin{cases}
\sinh(t)/t,&t\neq0,\\
1,&t=0.
\end{cases}
\]
For $p=u+v$ and $q=u-v$, define
\begin{equation}\label{eq:W}
W_y(u,v)=p^2\sinhc(yp)\Phi(u)\Phi(v),
\qquad 0\leq y\leq\frac12,
\end{equation}
and
\begin{equation}\label{eq:C}
C_y(x)=\iint_{\R^2}W_y(u,v)\cos(xq)\dd u\dd v.
\end{equation}
For $y>0$, this equals the form
\[
C_y(x)=\iint_{\R^2}
\frac{p\sinh(yp)}{y}\Phi(u)\Phi(v)\cos(xq)\dd u\dd v.
\]

Estimate \eqref{eq:decay} shows that
\[
|p|^a|q|^b e^{|p|/2}\Phi(u)\Phi(v)
\]
is integrable for every fixed pair of nonnegative integers $a,b$.  Thus all
integrals and derivatives used below converge absolutely and locally
uniformly.  Fubini's theorem, differentiation under the integral, and the
limits at $y=0$ and $y=\frac12$ are valid.

\begin{lemma}[Defect identity]\label{lem:defect}
Let
\[
E(z)=\Xi(z)+i\Xi'(z),
\qquad
E^{\#}(z)=\overline{E(\bar z)}.
\]
Then
\begin{equation}\label{eq:defect}
|E(x+iy)|^2-|E^{\#}(x+iy)|^2=2yC_y(x)
\end{equation}
for real $x$ and $0\leq y\leq\frac12$.
\end{lemma}

\begin{proof}
Put $s=\frac12-y$ and
\[
P(s,x)=\xi(s+ix)\xi(s-ix)=|\Xi(x+iy)|^2.
\]
Multiplying the Fourier integrals and symmetrizing under $u\leftrightarrow v$
and $(u,v)\mapsto(-u,-v)$ gives
\begin{equation}\label{eq:P-double}
P(s,x)=\iint_{\R^2}
\Phi(u)\Phi(v)\cosh(yp)\cos(xq)\dd u\dd v.
\end{equation}
Consequently,
\begin{equation}\label{eq:Py}
\frac{\partial P}{\partial y}(s,x)
=\iint p\sinh(yp)\Phi(u)\Phi(v)\cos(xq)\dd u\dd v
=yC_y(x).
\end{equation}

Because $\Xi$ is real entire,
$E^{\#}=\Xi-i\Xi'$.  Direct expansion yields
\[
|E|^2-|E^{\#}|^2
=-4\operatorname{Im}(\Xi'\overline{\Xi})
=2\frac{\partial}{\partial y}|\Xi(x+iy)|^2.
\]
Equation \eqref{eq:Py} proves \eqref{eq:defect}.
\end{proof}

At $y=0$, differentiation of \eqref{eq:Py} gives
\begin{equation}\label{eq:C0}
C_0(x)=2\left(\Xi'(x)^2-\Xi(x)\Xi''(x)\right).
\end{equation}

\section{Endpoint moments}

For $j\geq0$, define the raw moments
\begin{equation}\label{eq:A}
A_{2j}(y)=\iint_{\R^2}W_y(u,v)q^{2j}\dd u\dd v.
\end{equation}
Then
\begin{equation}\label{eq:C-derivatives}
C_y^{(2j)}(0)=(-1)^jA_{2j}(y),
\end{equation}
and $A_{2j}(y)>0$.

Define
\begin{equation}\label{eq:H}
H_{2j}(s)=\sum_{\ell=0}^{2j}(-1)^\ell
\binom{2j}{\ell}\xi^{(\ell)}(s)\xi^{(2j-\ell)}(s).
\end{equation}

\begin{lemma}[Moment identities]\label{lem:endpoints}
For $y>0$,
\begin{equation}\label{eq:A-H}
A_{2j}(y)=-\frac{H_{2j}'(\frac12-y)}{y}.
\end{equation}
The continuous endpoint values are
\begin{equation}\label{eq:endpoints}
A_{2j}(0)=H_{2j}''\!\left(\frac12\right),
\qquad
A_{2j}\!\left(\frac12\right)=-2H_{2j}'(0).
\end{equation}
\end{lemma}

\begin{proof}
Analytic continuation of \eqref{eq:fourier} gives
\[
\xi(s)=\int_{\R}\Phi(u)e^{(s-1/2)u}\dd u.
\]
Expanding $(u-v)^{2j}$ proves
\[
H_{2j}(s)=\iint_{\R^2}
e^{(s-1/2)p}q^{2j}\Phi(u)\Phi(v)\dd u\dd v.
\]
Equivalently, Leibniz differentiation gives
\[
\left.\partial_x^{2j}P(s,x)\right|_{x=0}=(-1)^jH_{2j}(s).
\]
Since $C_y=-P_s/y$, equations \eqref{eq:C-derivatives} and
\eqref{eq:A-H} follow.  The functional equation implies
\[
H_{2j}(1-s)=H_{2j}(s),
\qquad H_{2j}'(1/2)=0.
\]
Taylor expansion at $1/2$ gives the first endpoint formula; substituting
$y=1/2$ gives the second.
\end{proof}

\begin{lemma}[Strict raw-moment monotonicity]\label{lem:monotonicity}
For every $j\geq0$,
\[
0\leq y_1<y_2\leq\frac12
\quad\Longrightarrow\quad
A_{2j}(y_1)<A_{2j}(y_2).
\]
Consequently, with $m_{2j}(y)=A_{2j}(y)/A_0(y)$,
\begin{equation}\label{eq:cross-bounds}
\frac{A_{2j}(0)}{A_0(1/2)}
<m_{2j}(y)<
\frac{A_{2j}(1/2)}{A_0(0)}
\end{equation}
for every $y\in[0,1/2]$ and $j\geq1$.
\end{lemma}

\begin{proof}
For $p\neq0$,
\[
\sinhc(yp)=\sum_{r=0}^{\infty}
\frac{y^{2r}p^{2r}}{(2r+1)!}
\]
is strictly increasing for $y\geq0$.  The remaining factor in
\eqref{eq:A} is nonnegative and is positive away from measure-zero lines.
This proves strict monotonicity.  Applying the endpoint bounds separately to
the numerator and denominator gives \eqref{eq:cross-bounds}.  Equality would
require the numerator and denominator to attain opposite endpoints at the
same value of $y$, so both inequalities are strict even when $y$ is an
endpoint.
\end{proof}

\section{The degree-ten lower polynomial}

\begin{lemma}[Global cosine minorant]\label{lem:cosine}
For every real $r\neq0$,
\begin{equation}\label{eq:T10}
\cos r>
T_{10}(r):=
1-\frac{r^2}{2!}+\frac{r^4}{4!}-\frac{r^6}{6!}
+\frac{r^8}{8!}-\frac{r^{10}}{10!}.
\end{equation}
\end{lemma}

\begin{proof}
For $g=\cos-T_{10}$,
\[
g^{(10)}(r)=1-\cos r\geq0,
\]
and $g^{(k)}(0)=0$ for $0\leq k\leq9$.  Repeated integration proves
$g(r)\geq0$ for $r\geq0$.  The inequality is strict for $r>0$ because
$1-\cos r$ does not vanish identically on any interval $(0,r)$.  Evenness
handles negative $r$.
\end{proof}

For the five moments used below, set
\begin{equation}\label{eq:B}
\begin{aligned}
B_2&=\frac{A_2(1/2)}{A_0(0)},&
B_4&=\frac{A_4(0)}{A_0(1/2)},\\
B_6&=\frac{A_6(1/2)}{A_0(0)},&
B_8&=\frac{A_8(0)}{A_0(1/2)},\\
B_{10}&=\frac{A_{10}(1/2)}{A_0(0)}.
\end{aligned}
\end{equation}
Define
\begin{equation}\label{eq:Ptheta}
P_\theta(x)=
1-\frac{B_2x^2}{2!}+\frac{B_4x^4}{4!}
-\frac{B_6x^6}{6!}+\frac{B_8x^8}{8!}
-\frac{B_{10}x^{10}}{10!}.
\end{equation}

\begin{proposition}[Uniform polynomial lower bound]\label{prop:minorant}
For $0\leq y\leq\frac12$ and $x\neq0$,
\begin{equation}\label{eq:main-minorant}
\frac{C_y(x)}{A_0(y)}>P_\theta(x).
\end{equation}
\end{proposition}

\begin{proof}
Normalize $W_y\dd u\dd v$ by $A_0(y)$ and apply Lemma
\ref{lem:cosine}.  Strictness holds because $xq\neq0$ on a set of positive
measure.  We obtain
\[
\frac{C_y(x)}{A_0(y)}>
1-\frac{m_2(y)x^2}{2!}+\frac{m_4(y)x^4}{4!}
-\frac{m_6(y)x^6}{6!}+\frac{m_8(y)x^8}{8!}
-\frac{m_{10}(y)x^{10}}{10!}.
\]
For negative terms, use the upper bounds in \eqref{eq:cross-bounds}; for
positive terms, use the lower bounds.  This gives \eqref{eq:main-minorant}.
\end{proof}

\section{Certified endpoint arithmetic}

The certificate evaluates \eqref{eq:endpoints} from Taylor balls for
\begin{equation}\label{eq:xi-computational}
\xi(s)=(s-1)\pi^{-s/2}\Gamma(1+s/2)\zeta(s),
\end{equation}
which is algebraically identical to \eqref{eq:xi-definition} and analytic at
both centers $0$ and $1/2$.

Table \ref{tab:moments} lists ball centers.  At 269-bit Arb precision, the
largest radius among the twelve displayed values is $1.37\cdot10^{-67}$.

\begin{table}[ht]
\centering
\caption{Certified endpoint-moment ball centers.}
\label{tab:moments}
\scriptsize
\begin{tabular}{@{}c>{\raggedleft\arraybackslash}p{0.37\textwidth}>{\raggedleft\arraybackslash}p{0.37\textwidth}@{}}
\toprule
Moment & $A_{2j}(0)$ & $A_{2j}(1/2)$ \\
\midrule
$A_0$ & 0.02283966166888743667469247 & 0.02309570896612103381431025 \\
$A_2$ & 0.001890366586781360982949785 & 0.001909616896683607096775872 \\
$A_4$ & 0.000459720156209605774158694 & 0.000464013763611390134012507 \\
$A_6$ & 0.000182390894103604245533460 & 0.000183966337058884295480848 \\
$A_8$ & 0.000099156363571899705593806 & 0.000099954209940825929544209 \\
$A_{10}$ & 0.000067852553023503413540728 & 0.000068364291172414501807343 \\
\bottomrule
\end{tabular}
\end{table}

The resulting coefficient balls have centers
\begin{equation}\label{eq:B-values}
\begin{aligned}
B_2&=0.0836096840823574320891615416\ldots,\\
B_4&=0.0199050029979147510756695686\ldots,\\
B_6&=0.00805468748731450212309766654\ldots,\\
B_8&=0.00429328078723851344898443484\ldots,\\
B_{10}&=0.00299322696472082444610981628\ldots.
\end{aligned}
\end{equation}

Put $Q(t)=P_\theta(\sqrt t)$.  On $0\leq t\leq51$, the degree-four
Bernstein coefficient balls for $Q'$ have centers
\begin{equation}\label{eq:bernstein}
\begin{split}
&-0.0418048420411787160,\quad
-0.0206557763558942930,\\
&-0.0140554899445716895,\quad
-0.00787928068151705499,\\
&
-0.0159039318562651082.
\end{split}
\end{equation}
Every complete ball is negative.  Since Bernstein basis functions are
nonnegative on the unit interval, $Q'(t)<0$ for $0\leq t\leq51$.

For $t=51+r$, write
\[
Q'(51+r)=\sum_{j=0}^{4}c_jr^j.
\]
The coefficient-ball centers are
\begin{equation}\label{eq:tail-coefficients}
\begin{aligned}
c_0&=-0.0159039318562651082,\\
c_1&=-0.000629384405862592411,\\
c_2&=-0.0000327586169268804792,\\
c_3&=-0.000000415429458942178156,\\
c_4&=-0.000000004124265548832706.
\end{aligned}
\end{equation}
Again every complete ball is negative, so $Q'(t)<0$ for $t\geq51$.  Hence
\begin{equation}\label{eq:Q-monotone}
Q'(t)<0\qquad(t\geq0).
\end{equation}

The exact rational evaluation points satisfy the certified inequalities
\begin{align}
P_\theta(7.0362433)&>3.7223537277\cdot10^{-9}>0,
\label{eq:root-lower}\\
P_\theta(7.0362434)&<-1.7438217651\cdot10^{-8}<0.
\label{eq:root-upper}
\end{align}
Because $Q(0)=1$, \eqref{eq:Q-monotone} holds, and the leading coefficient
of $Q$ is negative, $P_\theta$ has exactly one positive zero.  Denote it by
$R_{10}$.  Then
\begin{equation}\label{eq:R10}
7.0362433<R_{10}<7.0362434,
\qquad
R_{10}=7.03624331759098920168\ldots.
\end{equation}

\begin{theorem}[Certified finite positivity band]\label{thm:main}
For every $0\leq y\leq\frac12$,
\begin{equation}\label{eq:finite-band}
C_y(x)>0\qquad(|x|\leq R_{10}).
\end{equation}
\end{theorem}

\begin{proof}
For $0<|x|<R_{10}$, Proposition \ref{prop:minorant} and
$P_\theta(x)>0$ prove the claim.  At $|x|=R_{10}$, strictness in
\eqref{eq:main-minorant} gives
\[
\frac{C_y(R_{10})}{A_0(y)}>P_\theta(R_{10})=0.
\]
At $x=0$, $C_y(0)=A_0(y)>0$.  Evenness in $x$ completes the proof.
\end{proof}

\section{Finite zero consequence}

\begin{corollary}\label{cor:zeros}
If $\rho$ is a nontrivial zero of $\zeta$ with
$|\operatorname{Im}\rho|\leq R_{10}$, then
\[
\operatorname{Re}\rho=\frac12.
\]
\end{corollary}

\begin{proof}
At a zero of $\Xi$, the two functions $E$ and $E^{\#}$ have the same
modulus, so the left side of \eqref{eq:defect} vanishes.  If
$\rho=\beta+i\gamma$ with $\beta<1/2$, then
\[
z=\gamma+i(1/2-\beta)
\]
satisfies $\Xi(z)=\xi(\rho)=0$ and $0<\operatorname{Im}z<1/2$.  For
$|\gamma|\leq R_{10}$, Theorem \ref{thm:main} and \eqref{eq:defect}
make the defect positive, a contradiction.  If $\beta>1/2$, the functional
equation and conjugation give the zero $1-\bar\rho$, with the same ordinate
and real part below $1/2$.
\end{proof}

At a real zero $x$ of $\Xi$, equation \eqref{eq:C0} becomes
$C_0(x)=2\Xi'(x)^2$.  Thus Theorem \ref{thm:main} also implies simplicity
of any real $\Xi$-zero in the finite interval, without assuming simplicity.

\section{Failure for a generic positive kernel}

The proof uses positivity and decay in its analytic steps, but the numerical
moment profile is specific to the Riemann kernel.  Consider
\begin{equation}\label{eq:counterexample}
\Phi_\varepsilon(u)=
\psi_\varepsilon(u-1)+\psi_\varepsilon(u+1)
+\frac{13}{6}\psi_\varepsilon(u),
\qquad
\psi_\varepsilon(u)=e^{-2\cosh(u/\varepsilon)}.
\end{equation}
This kernel is smooth, positive, even, and double-exponentially decreasing.
Its Fourier transform factors as
\begin{equation}\label{eq:counterexample-FT}
\widehat{\Phi_\varepsilon}(z)=
2\varepsilon K_{i\varepsilon z}(2)
\left(2\cos z+\frac{13}{6}\right).
\end{equation}
With $\lambda=\log(3/2)$, one has $2\cosh\lambda=13/6$, so
\[
z=(2k+1)\pi\pm i\lambda
\]
are exact nonreal zeros and $0<\lambda<1/2$.

The failure appears already in the normalized moments.  Let
$a=13/6$ and let $m_{2j}^{(\varepsilon)}(y)$ denote the moments formed from
\eqref{eq:counterexample}.  Scaling each of the three bumps and applying
dominated convergence gives, for $j\geq1$,
\[
\frac{A_{2j}^{(\varepsilon)}(y)}{\varepsilon^2M^2}
\longrightarrow 4a\sinhc y,
\qquad
M=\int_{\R}e^{-2\cosh t}\dd t,
\]
while
\[
\frac{A_0^{(\varepsilon)}(y)}{\varepsilon^2M^2}
\longrightarrow 8\sinhc(2y)+4a\sinhc y.
\]
Therefore
\begin{equation}\label{eq:counterexample-moments}
\lim_{\varepsilon\to0}m_{2j}^{(\varepsilon)}(y)
=\frac{a}{2\cosh y+a}.
\end{equation}
At $y=\lambda$, this limit is $1/2$, which violates the Riemann-kernel
bound $m_2(y)<B_2=0.0836096840\ldots$ for all small enough $\varepsilon$.
At $y=0$, the limit is $13/25$.

For $0<\varepsilon\leq1/4$, the same family also satisfies
\[
\Phi_\varepsilon(1/2)^2<
\Phi_\varepsilon(0)\Phi_\varepsilon(1),
\]
so it is not log-concave.  Neither positivity nor rapid decay supplies the
endpoint ratios in \eqref{eq:B}.

\section{The all-orders boundary}

The degree-ten theorem does not control the large-frequency sign of $C_y$.
The exact Taylor hierarchy makes the obstruction precise.  For $m\geq0$ set
\begin{equation}\label{eq:Sm}
S_m(y,x)=\sum_{j=0}^{2m+1}(-1)^j
\frac{m_{2j}(y)x^{2j}}{(2j)!}.
\end{equation}
The global Taylor inequality
$T_{4m+2}(r)<\cos r$ for $r\neq0$ gives
\begin{equation}\label{eq:Sm-lower}
S_m(y,x)<\frac{C_y(x)}{A_0(y)}
\qquad(x\neq0).
\end{equation}

\begin{proposition}[Exact hierarchy]\label{prop:exact-hierarchy}
Fix $\varepsilon>0$ and $R<\infty$.  Then $S_m$ converges uniformly to
$C_y(x)/A_0(y)$ on
\[
[\varepsilon,1/2]\times[-R,R].
\]
Moreover, $C_y(x)>0$ on this rectangle if and only if some $S_m$ is
uniformly positive there.
\end{proposition}

\begin{proof}
Estimate \eqref{eq:decay} gives a uniform exponential moment bound
\[
\sup_{\varepsilon\leq y\leq1/2}
\int e^{R|q|}\frac{W_y(u,v)}{A_0(y)}\dd u\dd v<\infty.
\]
Dominated convergence for the cosine series gives uniform convergence.  If
$C_y/A_0$ is positive on the compact rectangle, it has a positive minimum;
uniform convergence makes every sufficiently high section positive.  The
reverse implication follows from \eqref{eq:Sm-lower}, with the value at
$x=0$ equal to $1$.
\end{proof}

Thus divergence of the positivity radii for the exact sections is equivalent
to global open-strip positivity and supplies no weaker intermediate theorem.
The cross-endpoint hierarchy is more restrictive.  For $\varepsilon\geq0$,
define
\[
L_{2j}^{(\varepsilon)}=
\frac{A_{2j}(\varepsilon)}{A_0(1/2)},
\qquad
U_{2j}^{(\varepsilon)}=
\frac{A_{2j}(1/2)}{A_0(\varepsilon)},
\]
and
\begin{equation}\label{eq:Phat}
\widehat P_m^{(\varepsilon)}(x)=
1+
\sum_{\substack{1\leq j\leq2m+1\\ j\ \mathrm{even}}}
L_{2j}^{(\varepsilon)}\frac{x^{2j}}{(2j)!}
-
\sum_{\substack{1\leq j\leq2m+1\\ j\ \mathrm{odd}}}
U_{2j}^{(\varepsilon)}\frac{x^{2j}}{(2j)!}.
\end{equation}
Then
\[
\widehat P_m^{(\varepsilon)}(x)
<S_m(y,x)<\frac{C_y(x)}{A_0(y)}
\]
for $x\neq0$ and $\varepsilon\leq y\leq1/2$.  Theorem
\ref{thm:main} is the case $m=2$, $\varepsilon=0$.

Let $\widehat R_m^{(\varepsilon)}$ be the initial positivity radius of
\eqref{eq:Phat}.  The missing all-orders assertion is
\begin{equation}\label{eq:gap}
\sup_m\widehat R_m^{(\varepsilon)}=\infty
\qquad\text{for every }\varepsilon>0.
\end{equation}
Equation \eqref{eq:gap} would imply the Riemann Hypothesis.  The reverse
implication is not established: the lower polynomial combines pessimistic
numerator and denominator endpoints attained at different $y$-values.
Therefore \eqref{eq:gap} may be stronger than RH.  The present endpoint
identities do not provide the all-orders asymptotics needed to prove it.

\section{Reproducibility and certificate scope}

The public certificate evaluates Taylor balls for \eqref{eq:xi-computational}
at $0$ and $1/2$, forms \eqref{eq:H}, and extracts derivatives through order
$12$.  It uses \texttt{python-flint} 0.9.0, FLINT 3.6.0, 269-bit Arb precision, and a
formal-series cap of 18.  The cap exceeds the thirteen coefficients required
through degree 12.

The finite proof obligations are:
\begin{enumerate}
\item the twelve endpoint moment balls;
\item the five cross-endpoint ratios;
\item the five Bernstein signs in \eqref{eq:bernstein};
\item the five shifted-tail signs in \eqref{eq:tail-coefficients};
\item the two rational root-bracket signs.
\end{enumerate}
Arb implements midpoint-radius ball arithmetic with outward enclosures, so a
strict comparison succeeds only when the entire output ball lies on the
claimed side.  The computation uses no quadrature and no list of zeta zeros.
The analytic steps linking its finite values to $C_y$ are Lemmas
\ref{lem:defect}--\ref{lem:cosine} and Proposition \ref{prop:minorant}.

The repository records the exact dependency version, output, and SHA-256
checksums.  The command is
\begin{verbatim}
uv run --with python-flint==0.9.0 \
  python code/theta_moment_certificate.py
\end{verbatim}
Python optimization must remain disabled because program assertions encode
the sign obligations.

\section{Conclusion}

Endpoint derivatives of $\xi$ at $0$ and $1/2$, strict monotonicity of raw
moments, and a global cosine minorant produce an explicit lower polynomial for
$C_y/A_0$.  Arb certification of its coefficients and root proves the closed
finite band in Theorem \ref{thm:main}.  The argument supplies a reproducible
local validation of the endpoint-moment method.  It does not control the
all-orders radii in \eqref{eq:gap}, which remain the first unresolved step
toward unbounded open-strip positivity.

\section*{Disclosure and licensing}

OpenAI Codex assisted with document preparation, computational orchestration,
and consistency checks.  The named author retains responsibility for the
mathematical claims and the released artifacts.  The paper and associated
scholarly materials are Copyright \textcopyright{} 2026 Leonard van Hemert.
All rights reserved; full terms appear in the repository \texttt{NOTICE}.
Repository software and certification scripts are AGPL-3.0-only.

\begin{thebibliography}{99}

\bibitem{C2015}
G. Csordas,
\emph{Fourier transforms of positive definite kernels and the Riemann
$\xi$-function},
Comput. Methods Funct. Theory (2015),
\href{https://doi.org/10.1007/s40315-014-0105-8}{doi:10.1007/s40315-014-0105-8}.

\bibitem{CC2013}
M. W. Coffey and G. Csordas,
\emph{On the log-concavity of a Jacobi theta function},
Math. Comp. \textbf{82} (2013), 2265--2272,
\href{https://doi.org/10.1090/S0025-5718-2013-02681-6}{doi:10.1090/S0025-5718-2013-02681-6}.

\bibitem{CNV1986}
G. Csordas, T. S. Norfolk, and R. S. Varga,
\emph{The Riemann hypothesis and the Tur\'an inequalities},
Trans. Amer. Math. Soc. \textbf{296} (1986), 521--541,
\href{https://doi.org/10.1090/S0002-9947-1986-0846596-4}{doi:10.1090/S0002-9947-1986-0846596-4}.

\bibitem{CV1988}
G. Csordas and R. S. Varga,
\emph{Moment inequalities and the Riemann hypothesis},
Constr. Approx. \textbf{4} (1988), 175--198,
\href{https://doi.org/10.1007/BF02075457}{doi:10.1007/BF02075457}.

\bibitem{CV1989}
G. Csordas and R. S. Varga,
\emph{Fourier transforms and the Hermite--Biehler theorem},
Proc. Amer. Math. Soc. \textbf{107} (1989), 645--652,
\href{https://doi.org/10.1090/S0002-9939-1989-0982401-1}{doi:10.1090/S0002-9939-1989-0982401-1}.

\bibitem{CV1990}
G. Csordas and R. S. Varga,
\emph{Necessary and sufficient conditions and the Riemann hypothesis},
Adv. in Appl. Math. \textbf{11} (1990), 328--357,
\href{https://doi.org/10.1016/0196-8858(90)90013-O}{doi:10.1016/0196-8858(90)90013-O}.

\bibitem{PT2021}
D. J. Platt and T. S. Trudgian,
\emph{The Riemann hypothesis is true up to $3\cdot10^{12}$},
Bull. Lond. Math. Soc. \textbf{53} (2021), 792--797,
\href{https://doi.org/10.1112/blms.12460}{doi:10.1112/blms.12460}.

\end{thebibliography}

\end{document}
